Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-21 article/article.tex
Commit 2024-05-21 19:13

The use of the actual modeled values of clear sky GHI, described above ,
can not provide us with a robust method to distinguish the CE cases, due
to the limited accuracy of the input data. Our main focus was to
positively identify over irradiance events from CEs, so we created an
upper envelope of the clear sky irradiance,

\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots..

above which, any GHI value can safely attributed to CE. We evaluated the
performance of the modeled clear radiation for each of atmospheric level
of clearness, as reference, in order to conclude which is the most
appropriate.

To select the exact values of these thresholds factors (Equation
\ref{eq:CE4}), we implemented an empirical method, by manual inspection
of the CE identification, on specially selected days from the whole
dataset. We used seven sets of selected days, with characteristics
relevant to the efficiency of the identification threshold. These sets
were random groups of about 20 to 30 days with the following
characteristics: (a) the largest over irradiance CE events, (b) the
largest daily total over irradiance, (c) without clouds (by implementing
a clear sky identification algorithm as discussed in
\citet{Natsis2023}), (d) without clouds and without EC events, (e) with
at least \(60\,\%\) of the day length without clouds and some EC events,
(h) random days and (i) some manual selected days that were included
during the manual inspection. Where it was needed, for some of the edge
cases, we also used images from a sky-cam, to further aid the decisions
of the manual inspection.

After evaluating the modeled clear radiation for the different
atmospheric conditions, in relation to the measured GHI data, we choose
as a representative of the clear sky radiation, the case where
\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and
\(w_{h\text{cs}} = w_h - 1\sigma\) (\(\text{GHI}_\text{CSm}\)). These
values represent a typical atmosphere in Thessaloniki with low load of
aerosols and humidity, which are the main factor that attenuate the GHI,
excluding clouds. To create the limit of CE identification, we created a
two branched threshold, as a function of SZA. A constant factor for low
SZAs, and a higher ramped factor for higher SZAs
(Equation\nobreakspace\ref{eq:CE4}). This is the criterion of our CE
identification.

\begin{equation}
\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
\end{equation} where: \(\theta\) is the solar zenith angle, \(\text{E}\)
the measured irradiance, \(\text{E}_\text{CSm}\) the selected modelled
clear sky irradiance, and \(i\) each of the one-minute observation.

We have to note, that the differentiation of the threshold factor was
needed, because of the high irradiance values we observed, early in the
morning and late in the afternoon. We have confirmed, by inspecting
images from the sky cam, that we have duration of elevated irradiance,
either due to the clearness of the atmosphere, or some interferences by
reflections on nearby bright surfaces. Although, these cases may mask
some of the CE events. The actual CE events, produce higher irradiance
and thus are identified as such. As a side effect, the reported OIR will
be slight underestimated for those SZAs, but the overall contribution of
those cases to the total daily energy, is minimal due the low
occurrences and the lower irradiances.

>>>>

Our main focus was to positively identify over irradiance events related
to CEs. For this reason we had to select an appropriate set of
atmospheric parameterization, in Libradtran, and define an relevant
threshold for the CE identification. The selection of the atmospheric
parameterization will provide us with a reference, that has a good
agreement with the clear sky conditions. Additional, with the
implementation of the long term change, as described above, it will be
able to align well with most of the natural variation of the physical
quantity. The selection of adequate threshold, will also allow us to
have a robust method to distinguish the CE cases, which will compensate
for the limited accuracy of the input data, and the natural variability
of the atmosphere.

First, we evaluated the performance of the modelled clear radiation, for
each of the atmospheric level of clearness we have created as reference,
in relation to the measured GHI data, and choose as a representative of
the clear sky radiation, the case where
\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and
\(w_{h\text{cs}} = w_h - 1\sigma\) (\(\text{GHI}_\text{CSm}\)). These
values represent a typical atmosphere in Thessaloniki, with low load of
aerosols and humidity, which are the main factor that attenuate the GHI,
excluding clouds. To create the upper limit of CE identification, we
used a value relative to clear sky irradiance (\(4\,\%\)) with an
additional constant offset of \(15\,\text{W}/\text{m}^2\), as described
in Equation\nobreakspace\ref{eq:CE4}). \begin{equation}
\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation} where: \(\text{E}\) the measured irradiance,
\(\text{E}_\text{CSm}\) the selected modelled clear sky irradiance, and
\(i\) each of the one-minute observation. This is the criterion of our
CE identification.

In the process of defining the above details, we implemented an
empirical method, by manual inspection of the CE identification, on
specially selected days from the whole dataset. We used seven sets of
selected days, with characteristics relevant to the efficiency of the
identification threshold. These sets were random groups of about 20 to
30 days with the following characteristics: (a) the largest over
irradiance CE events, (b) the largest daily total over irradiance, (c)
without clouds (by implementing a clear sky identification algorithm as
discussed in \citet{Natsis2023}), (d) without clouds and without EC
events, (e) with at least \(60\,\%\) of the day length without clouds
and some EC events, (h) random days and (i) some manual selected days
that were included during the manual inspection. Where it was needed,
for some of the edge cases, we also used images from a sky-cam, to
further aid the decisions of the manual inspection.
